Learning \strips\ action models from {\em state-invariants}

### 2019-02-05 doc/ijcai-19-deductivelearning/deductivelearning.tex
first commit ijcai19 paper on deductive learning

\title{Learning \strips\ action models from {\em state-invaraints}}

@@

% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
% Check the ijcai19-multiauthor.tex file for detailed instructions
\author{
Diego Aineto$^1$\and
Sergio Jim\'enez$^1$\and
Eva Onaindia$^1$
\affiliations
$^1${\small Departamento de Sistemas Inform\'aticos y Computaci\'on. Universitat Polit\`ecnica de Val\`encia. Valencia, Spain}
\emails
{\scriptsize \{dieaigar,serjice,onaindia\}@dsic.upv.es, miquel.ramirez@unimelb.edu.au}}

@@

The specification of planning action models is a complex task, even for planning experts, which frequently causes a knowledge acquisition bottleneck that limits the potential of AI planning~\cite{kambhampati:modellite:AAAI2007}. The {\em machine learning} of action models aims to relieve this knowledge acquisition bottleneck. Nowadays there is a wide range of different approaches for learning planning action models~\cite{arora:amodels:ker2018}. However, most of these approaches aim maximizing some measure of {\em statistical consistency} over large sets of input examples that typically are sequential plans.

{\em Classical planning} is an interesting approach for learning \strips\ action models since it is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and guaranttees to output an action model that is {\em consistent} with the input knowledge~\cite{aineto2018learning}. In this paper we show that this flexibility of the compilation approach goes one step further since it also allows learning from {\em state-invariants}, logic formulae that constrain the set of possible states of a given domain. The experimental results show that {\em state-invariants} boost the performance of the {\em classical planing} compilation for learning \strips\ action models.

>>>>

\title{Learning \strips\ action models from {\em state-invariants}}

@@

% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
% Check the ijcai19-multiauthor.tex file for detailed instructions
\author{
Diego Aineto$^1$\and
Sergio Jim\'enez$^1$\and
Eva Onaindia$^1$
\affiliations
$^1${\small Departamento de Sistemas Inform\'aticos y Computaci\'on. Universitat Polit\`ecnica de Val\`encia. Valencia, Spain}
\emails
{\scriptsize \{dieaigar,serjice,onaindia\}@dsic.upv.es}}

@@

The specification of planning action models is a complex process that limits, too often, the potential of model-based planning systems~\cite{kambhampati:modellite:AAAI2007}. The {\em machine learning} of action models can relieve this knowledge acquisition bottleneck of AI planning and nowadays there exists a wide range of effective approaches for learning planning action models~\cite{arora:amodels:ker2018}. Most of current approaches for learning planning action models are {\em inductive}, meaning that they compute an action model that maximizes some notion of {\em statistical consistency} over a set of observations of plan executions so their success depends on the amount and quality of the input observations.

This paper proposes the exploitation of {\em deductive} knowledge to learn planning action models when input observations are minimal (just an {\em initial state} and the {\em goals}). We show that in such unfavourable scenario {\em state-invariant} (i.e logic formulae that specify constraints about the possible states of a given domain) help to learn better action models. Our approach is built on top of the {\em classical planning} compilation for the learning of \strips\ action models~\cite{aineto2018learning}. This compilation approach is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and guarantees to output an action model that is {\em consistent} with the input knowledge. In this paper we show how to push the flexibility of the compilation approach for learning of \strips\ action models and boost its performance with {\em state-invariant} when few observations are given as input.
